Challenges in Developing Great MCQMC Software

### 2022-07-14 MCQMC_2022_ChallengesDevelopSoftware.tex
Office Computer Updates

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-4ex}
	\begin{itemize}
		\item \textcite{LEc2017a} provides a history of \alert{random number generation}
		\item Notorious \alert{randu} from the 1960s \parencite{RANDU}, which fails the spectral test
		\item \alert{VEGAS} \parencite{Lep78a, Lep21a} importance sampling Monte Carlo algorithm favored by physicists
		\item \alert{ACM} low discrepancy point generators \parencite{BraFox88,BraFoxNie92,HonHic00a}
		\item \alert{FinDer} \parencite{PasTra95,FinDer} and \alert{BRODA} \parencite{BRODA20a} targeting quantitative finance
		\item Korobov cubature and scrambled Sobol' generators in \alert{NAG} \parencite{NAG27} for decades		
		\item Scrambled Sobol' and Halton generators in MATLAB \parencite{MAT9.13} since 2008, and fixed a few years later
	\end{itemize}
\end{frame}

\begin{frame}{Selective History of MC\textbf{QMC} Software}
	\vspace{-6ex}
	\begin{itemize}
		\item \alert{Stan} \parencite{STAN} for Markov Chain Monte Carlo (MCMC)
		\item Keller
		\item L'Ecuyer
		\item Nuyens
		\item Hickernell
		\item TensorFlow
		\item Scrambled Sobol' in SciPy \parencite{virtanen2020scipy} and PyTorch \parencite{paszke2019pytorch}

>>>>

\begin{frame}[allowframebreaks]{Selective History of MC\textbf{QMC} Software}
	\begin{itemize}
		\item \textcite{LEc2017a} provides a history of \alert{random number generation}
		\item Notorious \alert{randu} from the 1960s \parencite{RANDU}, which fails the spectral test
		\item \alert{VEGAS} \parencite{Lep78a, Lep21a} importance sampling Monte Carlo algorithm favored by physicists
		\item \alert{ACM} low discrepancy point generators \parencite{BraFox88,BraFoxNie92,HonHic00a}
		\item \alert{FinDer} \parencite{PasTra95,FinDer} and \alert{BRODA} \parencite{BRODA20a} targeting quantitative finance
		\item Korobov cubature and scrambled Sobol' generators in \alert{NAG} \parencite{NAG27} for decades		
		\item Scrambled Sobol' and Halton generators in \alert{MATLAB} \parencite{MAT9.13} since 2008, and fixed a few years later
		\item \alert{BUGS} \parencite{BUGSBook, BUGSweb} and \alert{Stan} \parencite{STAN} for Markov Chain Monte Carlo (MCMC)
		\item Low discrepancy generators \parencite{FriKel02,FriKelweb}, \alert{SamplePack} \parencite{SamplePack}, \textcite{Gru},  and \alert{MatBuilder} \parencite{paulin2022} by Alex Keller and collaborators
		\item L'Ecuyer
		\item Nuyens
		\item Giles
		\item Hickernell
		\item TensorFlow
		\item Scrambled Sobol' in SciPy \parencite{virtanen2020scipy} and PyTorch \parencite{paszke2019pytorch}
